Automated topic naming to support cross-project analysis of software maintenance activities

### 2011-01-22 msr/msr2011.tex
updated related work by moving it from unsupervised section.

The other approach is to extract concerns from software repositories.
Marcus et al.~\cite{marcus04wcre} describe their use of Latent Semantic Indexing (LSI) to identify commonly occurring concerns for software maintenance. The concerns are given by the user, and LSI used to retrieve them from a corpus. Topic modelling generates topics that are independent of a user query, and relate only to word frequencies in the corpus.
%Some results were interesting, but their precision was quite low. 
ConcernLines~\cite{treude09cl} shows tag occurrence using colour intensity. 
They mined 
developer created tags 
%change request tags (such as `milestone 3') and used these 
in order to analyze the evolution of a single product.
% make evolutionary analyses of a single product. 
The presence of a well-maintained set of tags is obviously essential to the success of this technique.

@@

>>>>

The other approach is to extract concerns from software repositories.
Marcus et al.~\cite{marcus04wcre} describe their use of Latent Semantic Indexing (LSI) to identify commonly occurring concerns for software maintenance. The concerns are given by the user, and LSI used to retrieve them from a corpus. Topic modelling generates topics that are independent of a user query, and relate only to word frequencies in the corpus.
%Some results were interesting, but their precision was quite low. 
With ConcernLines, \cite{treude09cl} shows tag occurrence using colour intensity. 
They mined 
developer created tags 
%change request tags (such as `milestone 3') and used these 
in order to analyze the evolution of a single product.
% make evolutionary analyses of a single product. 
The presence of a well-maintained set of tags is obviously essential to the success of this technique.

@@

% in our previous work~\cite{Hindle09ICSM}, as well as -- CITED a little too often (vanity cites!)
In Baldi et al.~\cite{Baldi2008}, topics are named manually: human experts read the highest-frequency members of a topic and assign a label accordingly. 
As discussed earlier, given the topic \emph{``listener change remove add fire''}, Baldi et al. would assign the label \emph{event-handling}. 
The labels are reasonable enough, but still require an expert in the field to determine them. 
Furthermore, these labels are project-specific, because they are generated from the data of that project. E.g., we might have a label called `Oracle' in the MySQL case, since Oracle owns MySQL.

This paper does this differently. First of all, we automated the process of naming the topics. Secondly, we labelled topics with project-independent terms, in order to permit cross-project comparison.
